Energy and the CES production function

### 2015-08-19 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Deleted unused lines.

  # Define the color palette (see http://www.cookbook-r.com/Graphs/Colors_(ggplot2))
  cbPalette <- c("#E69F00", "#999999", "#F0E442", "#56B4E9", "#009E73", "#0072B2", "#D55E00", "#CC79A7")
  # Make the plot
  plot <- ggplot(bar_chart_data, mapping=aes(x=label, y=value, fill=variable, width=0.4)) + 
    geom_bar(stat="identity") + 
    xlab("") +
    scale_x_discrete(limits=rev(order)) +
    ylab("") +
    scale_y_continuous(breaks=c(0, 0.5, 1)) + 
    guides(fill=guide_legend(title=NULL)) +
    coord_flip() + 
    scale_fill_brewer(palette="OrRd") +
    xy_theme() +
    theme(axis.ticks.y = element_blank())
  return(plot)
}
@

>>>>

  # Make the plot
  plot <- ggplot(bar_chart_data, mapping=aes(x=label, y=value, fill=variable, width=0.4)) + 
    geom_bar(stat="identity") + 
    xlab("") +
    scale_x_discrete(limits=rev(order)) +
    ylab("") +
    scale_y_continuous(breaks=c(0, 0.5, 1)) + 
    guides(fill=guide_legend(title=NULL)) +
    coord_flip() + 
    scale_fill_brewer(palette="OrRd") +
    xy_theme() +
    theme(axis.ticks.y = element_blank())
  return(plot)
}
@
